---
title: "Iris Dataset"
author: "Allan Lao"
output: html_document
---

##ctrl-alt-t for code blocks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Iris Dataset in R

The iris dataset is a built-in dataset in R that contains measurements on 4 different attributes (in centimeters) for 50 flowers from 3 different species.

This tutorial explains how to explore and summarize a dataset in R, using the iris dataset as an example

Load the Iris Dataset

```{r}
data(iris)
```

We can take a look at the first and last six and rows of the dataset by using the $head()$ and $tail()$ functions respectively:

```{r}
head(iris)
tail(iris)
```

Summarize the Iris Dataset

We can use the $summary()$ function to quickly summarize each variable in the dataset:

```{r}
summary(iris)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
